### 2017-05-12 02-background.tex
Gone over figures etc. Still need to redo related work.

SGLD originated from the Langevin Monte Carlo (LMC)~\cite{girolami2011riemann}, where unlike SGLD the gradient is computed exactly by using all data points. Then, Metropolis-Hastings accept-reject tests are applied. Comparing to LMC, SGLD only requires to process a mini-batch $\SGLDMinibatch$ at each iteration and ignores the MH test, and thus computation complexity substantially reduces from $\cO(N)$ to $\cO(n)$.

@@

\addtolength{\tabcolsep}{-3pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[b] % [htbp]
\center
\begin{tabular}{c C{0.075\textwidth} c L{0.26\textwidth}}
\textbf{symbol}
	 & \textbf{type} & \textbf{size} & \textbf{description} \\
         % & \multicolumn{1}{c}{\textbf{type}}
                           % & \multicolumn{1}{c}{\textbf{description}} \\
\hline
$\cK$      &              & $K$        & set of communities \\
\Vertices  & \{vertex\}   & $N$          & vertices in the graph \\
\Edges     & \{edge\}     &              & linked edges in the graph \\
$E$        & \{edge\}     &              & $\Vertices\times\Vertices$: linked and nonlinked edges \\
\Heldout   & \{edge\}     &              & held-out subset of the graph \\
\Minibatch & \{edge\}     &              & sampled mini-batch of edges in~$E$ \\
$M$        &              &              & number of vertices in \Minibatch \\
\Neighbors & \{vertex\}   &              & sampled neighbor set for a vertex in~\Minibatch \\
$\theta$   & float~vector 2-D & $K\times{}2$ & reparameterization of $\beta$.
					$\beta[k] = \theta[k][1] / \sum_j\theta[k][j]$ \\
$\beta$    & float vector & $K$          & community strength \\
$\phi$     & float~vector 2-D & $N\times{}K$ & reparameterization of $\pi$.
					$\pi[i][k] = \phi[i][k] / \sum_j\phi[i][j]$ \\
$\pi$      & float~vector 2-D & $N\times{}K$ &
					$\pi[i][k]$~is~probability that vertex $i$ is in community $k$ \\
\hline
\\[-3ex]
\end{tabular}
\caption{Definition of most important symbols}
\label{tbl-symbols}
\end{table}
\addtolength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.0}

>>>>

SGLD originated from Langevin Monte Carlo (LMC)~\cite{girolami2011riemann}, where unlike SGLD the gradient is computed exactly by using all data points. Then, Metropolis-Hastings accept-reject tests are applied. Comparing to LMC, SGLD only requires to process a mini-batch $\SGLDMinibatch$ at each iteration and ignores the MH test, and thus computation complexity substantially reduces from $\cO(N)$ to $\cO(n)$.

@@

\addtolength{\tabcolsep}{-3pt}
\renewcommand{\arraystretch}{1.5}
\begin{table}[tb] % [htbp]
\center
\begin{tabular}{c C{0.075\textwidth} c L{0.26\textwidth}}
\textbf{symbol}
	 & \textbf{type} & \textbf{size} & \textbf{description} \\
         % & \multicolumn{1}{c}{\textbf{type}}
                           % & \multicolumn{1}{c}{\textbf{description}} \\
\hline
$\cK$      &              & $K$        & set of communities \\
\Vertices  & \{vertex\}   & $N$          & vertices in the graph \\
\Edges     & \{edge\}     &              & linked edges in the graph \\
$E$        & \{edge\}     &              & $\Vertices\times\Vertices$: linked and nonlinked edges \\
\Heldout   & \{edge\}     &              & held-out subset of the graph \\
\Minibatch & \{edge\}     &              & sampled mini-batch of edges in~$E$ \\
$M$        &              &              & number of vertices in \Minibatch \\
\Neighbors & \{vertex\}   &              & sampled neighbor set for a vertex in~\Minibatch \\
$\theta$   & float~vector 2-D & $K\times{}2$ & reparameterization of $\beta$.
					$\beta[k] = \theta[k][1] / \sum_j\theta[k][j]$ \\
$\beta$    & float vector & $K$          & community strength \\
$\phi$     & float~vector 2-D & $N\times{}K$ & reparameterization of $\pi$.
					$\pi[i][k] = \phi[i][k] / \sum_j\phi[i][j]$ \\
$\pi$      & float~vector 2-D & $N\times{}K$ &
					$\pi[i][k]$~is~probability that vertex $i$ is in community $k$ \\
\hline
\\[-3ex]
\end{tabular}
\caption{Definition of most important symbols}
\label{tbl-symbols}
\end{table}
\addtolength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.0}

### 2017-05-12 gpu-05-evaluation.tex
Gone over figures etc. Still need to redo related work.

\begin{table}
  \centering
  \def\tabcolsep{0.2em}
  \begin{tabular}{l r r r p{9em}}
    Name            & \#Vertices &       \#Edges & \multicolumn{1}{c}{\#Ground-} & Description \\
                    &            &               & \multicolumn{1}{c}{truths}    &             \\
    \hline
    CA-HepPh        &    12,008  &    118,521    & \multicolumn{1}{c}{n/a}       & Paper citation network \\
    com-LiveJournal &  3,997,962 &    34,681,189 & 287,512        & Online blogging social network \\
    com-Friendster  & 65,608,366 & 1,806,067,135 & 957,154        & Online gaming social network \\
    com-Orkut       &  3,072,441 &   117,185,083 & 6,288,363      & Online social network \\
    com-Youtube     &  1,134,890 &     2,987,624 & 8,385          & Video-sharing social network \\
    com-DBLP        &    317,080 &     1,049,866 & 13,477         & Computer science bibliography collaboration network \\
    com-Amazon      &    334,863 &       925,872 & 75,149         & Product copurchasing network \\
    \hline
    \\[-1ex]
  \end{tabular}
  \caption{Summary of SNAP graph data sets used for evaluation.}
  \label{table-snap}
\end{table}

>>>>

\begin{table}
  \centering
  \def\tabcolsep{0.2em}
  \begin{tabular}{l r r r p{9em}}
    Name            & \#Vertices &       \#Edges & \multicolumn{1}{c}{\#Ground-} & Description \\
                    &            &               & \multicolumn{1}{c}{truths}    &             \\
    \hline
    CA-HepPh        &    12,008  &    118,521    & \multicolumn{1}{c}{n/a}       & Paper citation network \\
    com-LiveJournal &  3,997,962 &    34,681,189 & 287,512        & Online blogging social network \\
    com-Friendster  & 65,608,366 & 1,806,067,135 & 957,154        & Online gaming social network \\
    com-Orkut       &  3,072,441 &   117,185,083 & 6,288,363      & Online social network \\
    com-Youtube     &  1,134,890 &     2,987,624 & 8,385          & Video-sharing social network \\
    com-DBLP        &    317,080 &     1,049,866 & 13,477         & Computer science bibliography network \\
    com-Amazon      &    334,863 &       925,872 & 75,149         & Product copurchasing network \\
    \hline
    \\[-1ex]
  \end{tabular}
  \caption{Summary of SNAP graph data sets used for evaluation.}
  \label{table-snap}
\end{table}
